---
title: "group_assignment_7"
format: html
editor: visual
---

## Authors

**Emilie Leonora Wenner** s193602\
**Jonas Sennek Rasmussen** s203516\
**Iben Nordentoft Sommerand** s203522\
**Vedis Marie Kühnau Arntzen** s203546\
**Torbjørn Gøbel Bak Regueira** s203555

## Loading libraries

```{r}
#| label: "loading_libraries"
#| echo: true
#| eval: true
#| output: false

library("tidyverse")
library("broom")
library("cowplot")

```

## Getting the data

```{r}

biopsy <- read_csv("https://wilkelab.org/classes/SDS348/data_sets/biopsy.csv")
```

## Look at the data in PC coordinates 1

## Look at the data in PC coordinates 2

## Look at the variance explained by each PC

We will plot the variance explained by each PC. First, we need to extract the information:

```{r}

pca_fit %>%
  tidy(matrix = "eigenvalues")
```

And then we plot:

```{r}

pca_fit %>%
  tidy(matrix = "eigenvalues") %>%
  ggplot(aes(PC, percent)) +
  geom_col(fill = "#56B4E9", alpha = 0.8) +
  scale_x_continuous(breaks = 1:9) +
  scale_y_continuous(
    labels = scales::percent_format(),
    expand = expansion(mult = c(0, 0.01))
  ) +
  theme_minimal_hgrid(12)

```

The first PC captures 65% of variation.
