---
title: "group_assignment_7"
format: html
editor: visual
---

## Authors

**Emilie Leonora Wenner** s193602\
**Jonas Sennek Rasmussen** s203516\
**Iben Nordentoft Sommerand** s203522\
**Vedis Marie Kühnau Arntzen** s203546\
**Torbjørn Gøbel Bak Regueira** s203555

## Loading libraries

```{r}
#| label: "loading_libraries"



```

## Look at the data in PC coordinates 1

```{r}
pca_fit <- biopsy %>% 
  select(where(is.numeric)) %>% # retain only numeric columns
  prcomp(scale = TRUE) # do PCA on scaled data

```

Alternatively,

```{r}
pca_fit <- biopsy %>% 
  select(where(is.numeric)) %>% # retain only numeric columns
  scale() %>% # scale data
  prcomp() # do PCA
```

Now we plot the data in PC coordinates

```{r}
  augment(biopsy) %>% # add original dataset back in
  ggplot(aes(.fittedPC1, .fittedPC2, color = outcome)) + 
  geom_point(size = 1.5) +
  scale_color_manual(
    values = c(malignant = "#D55E00", benign = "#0072B2")
  ) +
  theme_half_open(12) + background_grid()
```

## Look at the data in PC coordinates 2

Now we get the rotation matrix

```{r}

# extract rotation matrix
pca_fit %>%
  tidy(matrix = "rotation")
```

Which we can plot

```{r}
# define arrow style for plotting
arrow_style <- arrow(
  angle = 20, ends = "first", type = "closed", length = grid::unit(8, "pt")
)

# plot rotation matrix
pca_fit %>%
  tidy(matrix = "rotation") %>%
  pivot_wider(names_from = "PC", names_prefix = "PC", values_from = "value") %>%
  ggplot(aes(PC1, PC2)) +
  geom_segment(xend = 0, yend = 0, arrow = arrow_style) +
  geom_text(
    aes(label = column),
    hjust = 1, nudge_x = -0.02, 
    color = "#904C2F"
  ) +
  xlim(-1.25, .5) + ylim(-.5, 1) +
  coord_fixed() + # fix aspect ratio to 1:1
  theme_minimal_grid(12)
```

## Look at the variance explained by each PC
